---
title: "Blog Post Krishna"
author: "Krishna Chaitanya Rao"
desription: "Something to describe what I did"
date: "08/04/2022"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true
categories:
  - hw1
  - weekly challenge
  - my name
  - dataset
  - ggplot2
---

```{r setup, echo=FALSE}
library(tidyverse)

```

## Instructions

This document provides yaml header inforamtion you will need to replicate each week to submit your homework or other blog posts. Please observe the following conventions:

-   Save your own copy of this template as a blog post in the `posts` folder, naming it `FirstLast_hwX.qmd`
-   Edit the yaml header to change your author name - use the same name each week
-   include a *description* that is reader friendly
-   update the *category* list to indicate the type of submission, the data used, the main packages or techniques, your name, or any thing else to make your document easy to find
-   edit as a normal qmd/rmd file


```{r}
x <- c(2,3,4,5)
mean(x)
```

## Rendering your post

```{r}
library(readr)
animal_weight <- read_csv("/Users/krishnachaitanyarao/Desktop/dacss601_august2022//_data/animal_weight.csv")
View(animal_weight)

```
```{r}
plot(animal_weight$Buffaloes)
```

